---
title: "Analysis script for identifying the best predictors of biomass for 13 plant species"
author: "Sunyoung Park"
date: "04/22/2023"
output: html_document
---


This Quarto file loads the cleaned data and does some initial analysis. 



# Analysis 

In this analysis script, I am analyzing direct measurements of 11 different morphological characteristics and aboveground biomass to identify the best non-destructive indicators for the aboveground biomass of each of the 13 plant species.  

I am using regression analysis to perform my analysis. 


# Setup

```{r }
#| cache = FALSE
knitr::read_chunk('statistical_analysis.R')
```

Load needed packages and filepaths.  

```{r setup}
#| message: FALSE
#| warning: FALSE
```

Load custom functions.

```{r functions}
```

Load the data.

```{r loaddata}
```



# Results of the data analysis

The results were created by the `statistical_analysis.R` script and to the `Results` folder.


```{r testfornormality}
``` 

# 1. Aptenia cordifolia

```{r linear_regression_model_A.cordifolia}
``` 

# 2. Artemisia californica

```{r linear_regression_model_A.californica}
``` 

# 3. Chondropetalum tectorum

```{r linear_regression_model_C.tectorum}
``` 

# 4. Gnaphalium spp.

```{r linear_regression_model_Gnaphalium.spp.}
``` 

# 5. Rhus integrifolia

```{r linear_regression_model_R.integrifolia}
``` 

# 6. Solidago spp.

```{r linear_regression_model_Solidago.spp.}
``` 

#7. Unidentified shrub 

```{r linear_regression_model_unidentifiedshrub}
``` 

# 8. Baccharis pilularis

```{r linear_regression_model_B.pilularis}
``` 

# 9. Euphorbia spp.

```{r linear_regression_model_Euphorbia.spp.}
``` 

# 10. Lactucca spp.

```{r linear_regression_model_Lactucca.spp.}
``` 

# 11. Onetheria biennis

```{r linear_regression_model_O.biennis}
``` 