---
title: "Cleaning R script for identifying the best predictors of biomass for 13 plant species"
author: "Sunyoung Park"
date: "2023-04-21"
output: html_document
---

# Processing script (data cleaning) with code pulled in from script

This quarto file documents the data cleaning of the raw data `plant_measurement_raw.csv` in the raw data folder `../../Data/Raw_data/`. The clean data file is named `processeddata.rds` and also saved in `.csv` formats.

To run this code, run `quarto preview processingfile.qmd` from the Processing code directory `project_root/Code/Processing_code`.  Alternatively, you can prepend the relative path to the file from your current working directory. To generate the `.html` output, change  `quarto preview` to `quarto render`.

# Setup

This code is needed to pull the code chunks contained in `processingcode.R` into active memory:

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('processingcode.R')
```

Load needed packages (from the `packages` code chunk):

```{r, packages, message = FALSE, warning = FALSE}
```


# Data loading

```{r, loaddata1.1}
```

I am using check.names=F because these names have spaces and parentheses and I want to preserve the original names.

```{r, loaddata1.2}
```

```{r, loaddata1.3}
```


# Explore Data


```{r, exploredata}
```

```{r, exploredata2}
```


# Cleaning


```{r, cleandata1}
```

```{r, cleandata2}
```

```{r, cleandata3}
```

```{r, cleandata4}
```


# Save data


```{r, savedata}
```


```{r, savedata2}
```








